\documentclass{article}

\include{libs.tex}
\include{cards.tex}

\begin{document}
\card[type=cantrip,time=action,components=SV]{Eldritch Blast}
    {A beam of crackling energy streaks toward a creature within range. Make a ranged spell Attack against the target. On a hit, the target takes 1d10 + 3 (Char by Agonizing Blast) force damage.
    \\[1mm]
    At Higher Levels. The spell creates more than one beam when you reach higher levels: two beams at 5th level, three beams at 11th level, and four beams at 17th level. You can direct the beams at the same target or at different ones. Make a separate attack roll for each beam.}
    {120 feet\\Instantaneous}%
\card[time=reaction, type=scroll]{Hellish Rebuke}
    {You point your finger, and the creature that damaged you is momentarily surrounded by hellish flames. The creature must make a Dexterity saving throw.
    \\[1mm]
    It takes 4d10 + 3 (2d10 + 1d10 for each level over 1, +3 for char by radiant soul) fire damage on a failed save, or half as much damage on a successful one.}
    {60 feet\\Instantaneous}%
\card[time=action, type=cantrip,components=SV]{Sacred Flame}
    {Flame-like Radiance descends on a creature that you can see within range. The target must succeed on a Dexterity saving throw or take 1d8 + 3 (Char by Radiant Soul) radiant damage.
    \\[1mm]
    The target gains no benefit from cover for this saving throw.}
    {60 feet\\Instantaneous}%
    
\card[time=action, type=spell, components=SV, cost=1st]{Hex}
    {You place a curse on a creature that you can see within range. Until the spell ends, you deal an extra 1d6 necrotic damage to the target whenever you hit it with an attack. Also, choose one ability when you cast the spell. The target has disadvantage on ability checks made with the chosen ability. 
    \\[1mm]
    If the target drops to 0 hit points before this spell ends, you can use a bonus action on a subsequent turn of yours to curse a new creature.
    \\[1mm]
    A Remove Curse cast on the target ends this spell early.}
    {60 feet\\Concentration up to 8h}%
\card[time=10 min, type=ritual, font size=4.2, cost=10 gp,components=MSV]{Find Familiar (1/2)}
    {You gain the service of a familiar, a spirit that takes an animal form you choose: bat, cat, crab, frog (toad), hawk, lizard, octopus, owl, poisonous snake, fish (quipper), rat, raven, sea horse, spider, or weasel. Appearing in an unoccupied space within range, the familiar has the statistics of the chosen form, though it is a celestial, fey, or fiend (your choice) instead of a beast.
    \\[1mm]
    Your familiar acts independently of you, but it always obeys your commands. In combat, it rolls its own initiative and acts on its own turn. A familiar can’t attack, but it can take other actions as normal.
    \\[1mm]
    When the familiar drops to 0 hit points, it disappears, leaving behind no physical form. It reappears after you cast this spell again. As an action, you can temporarily dismiss your familiar to a pocket dimension. Alternatively, you can dismiss it forever. As an action while it is temporarily dismissed, you can cause it to reappear in any unoccupied space within 30 feet of you. Whenever the familiar drops to 0 hit points or disappears into the pocket dimension, it leaves behind in its space anything it was wearing or carrying.}
    {10 feet\\Instantaneous}%
\card[time=10 min, type=ritual, font size=4.5, cost=10 gp,components=MSV]{Find Familiar (2/2)}
    {While your familiar is within 100 feet of you, you can communicate with it telepathically. Additionally, as an action, you can see through your familiar’s eyes and hear what it hears until the start of your next turn, gaining the benefits of any special senses that the familiar has. During this time, you are deaf and blind with regard to your own senses.
    \\[1mm]
    You can’t have more than one familiar at a time. If you cast this spell while you already have a familiar, you instead cause it to adopt a new form. Choose one of the forms from the above list. Your familiar transforms into the chosen creature.
    \\[1mm]
    Finally, when you cast a spell with a range of touch, your familiar can deliver the spell as if it had cast the spell. Your familiar must be within 100 feet of you, and it must use its reaction to deliver the spell when you cast it. If the spell requires an attack roll, you use your attack modifier for the roll.}
    {10 feet\\Instantaneous}%


\end{document}
